GSE158420: RNA expression downsampling

### 2024-07-17 analysis/GSE158420_rna.Rmd
cores

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("HGNChelper")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("gplots")
  library("gridExtra")
  library("png")
  library("fgsea")
  library("parallel")
})

@@

>>>>

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("HGNChelper")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("gplots")
  library("gridExtra")
  library("png")
  library("fgsea")
  library("parallel")
  library("RhpcBLASctl")
})

@@

RhpcBLASctl::blas_set_num_threads(4) #set automatic cores to 1
